Ignition of Fuel Beds by Firebrands

### 2022-04-15 litreview.tex
Updated introduction on models.

    Proposed ignition models that provide greater accuracy than the hot spot and critical mass flux models do so at the expense of complexity and computational cost. One of the most recent, and most promising, tools for ignition modeling has been developed by Lautenberger and is a customized computational fluid dynamic model.

>>>>

    Proposed ignition models that provide greater accuracy than the hot spot and critical mass flux models do so at the expense of complexity and computational cost. The majority of these models and modelling efforts use a two part approach to join a pyrolysis specific solver to address the chemical kinetics of pyrolysis to an existing or custom computation fluid dynamics solver. This approach requires selecting choosing a combination of three parts each of which has limitations and considerations which may affect the accuracy of ignition predictions. First an appropriate chemical kinetic mechanism must be chosen based on the computational resources available. For example, many early works~\cite{DiBlasi1996} and some more recently~\cite{Ding2015, Torero2020} have considered pyrolysis occurring as a single step process or as a process of few reactions (approximately ten or fewer). Newer kinetic mechanisms have been developed to more completely capture the processes of pyrolysis and are much more complex. Perhaps the most complete mechanisms are extended forms of the mechanism developed by Ranzi et al.~\cite{Ranzi2008}. Additions to this mechanism have expanded the method to include extractives to cover a greater variety of biomass~\cite{Debiagi2015} and the addition of reactions to address gas phase reactions previously not considered~\cite{Dhahak2019}.

    One of the most recent, and most promising, tools for ignition modeling and pyrolysis is Gpyro which is a pyrolysis solver specifically designed ~\cite{Lautenberger2009a}. Unlike other
